Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-28 apples_and_oranges.qmd
several changes with percent variable

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_baseline_sd_active = (baseline_sd_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_baseline_sd_control = (baseline_sd_control - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_sd_active = (post_sd_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_sd_control = (post_sd_control - scale_min) / (scale_max - scale_min))

@@

# count studies - same as for overall sample
n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) 
df_count_studies <- count_studies(df_long_for_metan )

# specify model
model_1 <- as.formula(~ four_level_var + perc_baseline_mean )

# run metareg function 
# here you can use the simulated results directly
list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated, model_1)

@@

>>>>

df_appl_v_orange <- df_appl_v_orange %>% 
  mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this #is the best way to estimate the SD of the linear transform of the percentage

  mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_baseline_sd_control = baseline_sd_control  / (scale_max - scale_min)) %>% 
  mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_sd_active = post_sd_active  / (scale_max - scale_min)) %>% 
  mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
  mutate(perc_post_sd_control = post_sd_control  / (scale_max - scale_min))

@@

# the first thing to do is to create a new dataset with the percentage cohen's d

list_df_simulated_percentage <- list_df_simulated

for(i in 1: length(list_df_simulated_percentage)){

  list_df_simulated_percentage[[i]]$cohens_d <- 
            (list_df_simulated_percentage[[i]]$perc_post_mean - list_df_simulated_percentage[[i]]$perc_baseline_mean)/
    ((list_df_simulated_percentage[[i]]$perc_post_sd + list_df_simulated_percentage[[i]]$perc_baseline_sd)/2)

# specify model
model_1 <- as.formula(~ four_level_var )

# run metareg function 
# here you can use the simulated results directly
list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_1)

@@

##### now for the baseline controlled variable
# specify model
model_2 <- as.formula(~ four_level_var + perc_baseline_mean )

# run metareg function 
# here you can use the simulated results directly
list_model_2_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_2)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_perc_mod_2 <-  aggregate_model_results(list_model_2_meta_reg_perc, condition)
aggregate_results_perc_mod_2 <- cbind(aggregate_results_perc_mod_2, condition)

# extract SMDs from the  list
means_perc_mod_2 <-  lapply(list_model_2_meta_reg_perc, extract_coefficients_func)

# calculate mean SMDs and ses
df_mean_coefs_perc_mod_2 <- calculate_mean_coefs_ses(means_perc_mod_2, condition)
df_mean_coefs_perc_mod_2 <- data.frame(cbind(condition,df_mean_coefs_perc_mod_2))

# add the ns
df_mean_coefs_perc_mod_2 <- data.frame(cbind(df_mean_coefs_perc_mod_2, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
